Free surface computations in mantle convection models

### 2015-11-02 free-surface-paper.tex
Unicode issue
Add a couple of sentences on comparison

\fntext[ref3]{\url{heister@clemson.edu}, partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation under Award No. EAR-0949446 
and The University of California—Davis, and National Science Foundation grant DMS1522191.}

@@

Figure~\ref{fig:timestep_convergence}b shows the convergence of the quasi-implicit scheme with timestep.
When $\theta=0.0$, it corresponds to the unstabilized forward Euler scheme, and is first order in time. 
When $\theta=1.0$ it is also first order in time, but allows for a much larger timestep.  When $\theta=0.5$
the quasi-implicit guess for the body force is good enough that it actually seems to achieve the second-order 
convergence of a trapezoidal scheme, though it is not clear whether this extends to more complicated models.

@@

The normal mode perspective on the problem also provides insights into the effect of 
the quasi-implicit stabilization scheme proposed by \citet{kaus2010stabilization}.
The relaxation time of each mode is lengthened by an amout $\theta \Delta t$, and the
maximum allowable timestep is correspondingly lengthened.

>>>>

\fntext[ref3]{\url{heister@clemson.edu}, partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation under Award No. EAR-0949446 
and The University of California-Davis, and National Science Foundation grant DMS1522191.}

@@

Figure~\ref{fig:timestep_convergence}b shows the convergence of the quasi-implicit scheme with timestep.
When $\theta=0$, it corresponds to the unstabilized forward Euler scheme, and is first order in time. 
When $\theta=1$ it is also first order in time, but allows for a much larger timestep.  When $\theta=0.5$
the quasi-implicit guess for the body force is good enough that it actually seems to achieve the second-order 
convergence of a trapezoidal scheme, though it is not clear whether this extends to more complicated models.

@@

The normal mode perspective on the problem also provides insights into the effect of 
the quasi-implicit stabilization scheme proposed by \citet{kaus2010stabilization}.
The relaxation time of each mode is lengthened by an amount $\theta \Delta t$, and the
maximum allowable timestep is correspondingly lengthened.

It is not clear that the non-standard finite difference scheme is superior to 
the quasi-implicit scheme. For $\theta=0.5$ the quasi-implicit scheme is more accurate,
but is only conditionally stable. For $\theta=1$ the two schemes are comparably accurate 
in the tests we ran.
